It's no secret that
real-world problems involve graph-structured data.
An important characteristic of graphs are their 
degree of \emph{homophily},
referring to the tendency for nodes with
similar features to be closely connected \citep{li2023homogcl}.
For instance, in a professional network
(a high-homophily graph),
people tend to be connected with similar individuals
(e.g. industry, position, years of experience).
Low-homophily graphs are an important subset of graphs in
practice, including device IOT graphs and 
specific social media communities.
As we explore the literature,
it becomes evident that learning low-homophily graphs
has presented challenges 
in performance and computational complexity.

\subsection{Related Works}
\input{src/related}

\subsection{Problem Statement}

In this paper we address the problem of balancing
high performance and computational efficiency
for low-homophily graph learning.
We are particularly interested in 
bridging the gap between the literature of
sparse SA for GTs (e.g. \textsc{Exphormer}),
and the bleeding edge performance of \textsc{GCN-SA}.

\subsection{Our Contributions}

We offer a focused study of sparse SA
techniques applied to the \textsc{GCN-SA} architecture.
We perform experiments to determine 
whether GCN-SA, modified 
with various sparse SA mechanisms,
improves runtime while
maintaining similar classification accuracy.
We compare 2 baselines GCN and GCN-SA against 
2 GCN-SA models modified with sparse SA 
(\textsc{BigBird}, \textsc{Exphormer}).
Analysis is performed on 8 datasets of varying homophily.
% Our results demonstrate the ability for GCN-SA to learn 
% on \emph{large} low-homophily graphs, 
% which has broad practical applications.
% The source code for this project
% is hosted at
% \texttt{github.com/chenanton/sparse-gcn-sa}.
